Interval Probability for Fuzzy Quantum Theories

### 2016-06-30 prob.tex
"Referenece\O. Nikodym, Sur une généralisation des intégrales de M. J. Radon.pdf" Added...

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by $\pmeas(E)=\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in E}}\rho(\omega)$,
where $\rho:\Omega\rightarrow[0,1]$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in\Omega}}\rho(\omega)=1$.
Furthermore, every probability measure~$\pmeas$ can be written in
this form for an unique $\rho$~\cite{Kolmogorov1950,Swart2013}
which is called the probability distribution~\cite{GrahamKnuthPatashnik1994}.

>>>>

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by $\pmeas(E)=\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in E}}\rho(\omega)$,
where $\rho:\Omega\rightarrow[0,1]$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in\Omega}}\rho(\omega)=1$.
Furthermore, every probability measure~$\pmeas$ can be written in
this form for an unique $\rho$~\cite{Kolmogorov1950,Swart2013}
which is called the probability distribution~\cite{GrahamKnuthPatashnik1994}
or the Radon-Nikodym derivative of $\pmeas$ with respect to the counting
measure~\cite{Nikodym1930,Torchinsky1994}.
